### 2013-11-23 tests_Housing.Rmd
added non regularized data (Abalone & Housing)

```{r}
set.seed(121)

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=100, lambda=0.8, runs=25)

@@

save(report, file="Housing300_lambda0.8.Rda") # recover with load("Housing300.Rda")

@@

write.table(df, "Housing300_lambda0.8.txt")

>>>>

```{r}
set.seed(321)

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=100, lambda=1, runs=25)

@@

save(report, file="Housing300_lambda1.Rda") # recover with load("Housing300.Rda")

@@

write.table(df, "Housing300_lambda1.txt")
